Title

### 2012-12-04 inc/photocathode/plasmon/plasmon.tex
include PAPE data and PAPE explaination (that from 2010 ANL report)

\subsection{Introduction}

@@

\subsection{Experimental Attempts}

\subsubsection{Commerical Grating on Glass}

@@

\subsubsection{Sinusoidal Grating}

@@

Collaborators at Argonne National Laboratory's Electron Microscopy Center, Material Science Division used a defocused Zeiss 1540XB focused ion beam (FIB) to iteratively mill an approximately sinusoidal shape into the surface of a silicon wafer.
Several regions were created each 100x100$\mu$m in area, having a $\sim$1$\mu$m period and $\sim$10\% modulation depth.
An SEM image of one such region is shown in \ref{fig:fib-si-sem}.

@@

\begin{figure}
  \centering
  \includegraphics{HighMagSEM.jpg}
  \caption{
    SEM image of sinusoidal grating on silicon.
    Pattern milled by Focused Ion Beam (FIB) milling at Argonne National Lab (ANL).
    Sample was later coated with 300 nm gold film.
  }
  \label{fig:fib-si-sem}
\end{figure}

\subsubsection{Sinusoidal Grating, Rotated}

\subsubsection{Trenched Grating}

>>>>

@@

\subsection{Commerical Grating on Glass}

@@

\subsection{Sinusoidal Grating}

@@

Collaborators at Argonne National Laboratory's Electron Microscopy Center, Material Science Division used a defocused Gallium focused ion beam (FIB) (Zeiss 1540XB) to iteratively mill an approximately sinusoidal shape into the surface of a silicon wafer.
Several regions were created each 100x100$\mu$m in area, having a $\sim$1$\mu$m period and $\sim$10\% modulation depth.
Given a laser wavelength of 523nm ($\varepsilon_{Au} \approx –3.95$ \cite{johnson_optical_1972}), this choice of periodicity corresponds by \ref{eq:plasmon_condition} to an incidence angle of $\sim39^{\circ}$, which is within the acceptance range of our experimental setup (35-75$^{\circ}$). %TODO point to Togawa section
An SEM image of one such region is shown in \ref{fig:fib-si-sem}.

\begin{figure}
  \centering
  \includegraphics{HighMagSEM.jpg}
  \caption{
    SEM image of sinusoidal grating on silicon.
    Pattern milled by focused ion beam milling at Argonne National Lab.
    Sample was later coated with 300 nm gold film.
  }
  \label{fig:fib-si-sem}
\end{figure}

@@

\begin{figure}
  \centering
  \input{power_seq}
  \caption{}
  \label{fig:pape}
\end{figure}

% Content taken from 2010 ANL report
Strong enhanced phototemission was observed for only a narrow $\pm$5mrad range of incidence angles $\theta$ around the expected plasmon resonance angle of 39$^{\circ}$.
Moreover, this enhanced laser-driven electron emission was only observed for $p$-polarized incident 523nm femtosecond laser radiation.
These two properties are known characteristics of plasmon-assisted photoemission.

As seen in \ref{fig:pape}, at low incident laser intensities, below about 25MW/cm$^2$, the emission from the nano-patterned photocathode at the plasmon resonance condition is very similar to that observed from a flat gold surface neighboring the FIB-milled region.
Specifically, the strength of both emissions have a quadratic dependence on the incident laser intensity.
This is consistent with a two-photon field emission process --- it requires the absorption of two 2.37eV (green) photons for an electron to acquire sufficient energy to allow any significant field emission as gold has a work function of 5.1eV.
Moreover, both emissions have similar momentum distributions \fixme{(images A and E)}, again indicating a similar emission process.
The only difference is that the emission from the nano-patterned region is 3-4 times more efficient.
This is readily explained by the fact that the periodic surface modulation results in a local enhancement of the $\sim$1MV/m DC gun field at the peaks of the modulation which, through the Schottky effect, then presents a reduced barrier for field emission.

Above $\sim$32MW/cm$^2$, there is a rapid and dramatic increase in the emission efficiency for the nano-patterned photocathode.
This can be explained by a suppression of the barrier to photoemission below the two-photon excitation energy, thus allowing direct two-photon photoemission.
This is likely caused by the laser-excited surface plasmon since a similar increase from the neighboring flat gold surface is not present.
The observed distinct changes in the momentum distributions \fixme{(images B and C)} in this laser intensity range support this argument.
In \fixme{image B}, at a laser intensity of $\sim$30MW/cm$^2$, there is already a distinct broadening of the momentum distribution in the direction parallel to the wavevector $k_G$ of the sinusoidal modulation on the photocathode (i.e., perpendicular to the FIB-milled grooves). 
This broadening becomes the dominant feature of the electron emission above $\sim$32MW/cm$^2$; indeed, it becomes so severe that at laser intensities above $\sim$37MW/cm$^2$ the 6mm-diameter bore of the magnetic lenses becomes a strong limiting aperture for the resulting beam --- as is clearly seen in \fixme{image D} and by the cut-off in the detected electron signal (YAG fluorescence).

\subsection{Sinusoidal Grating, Rotated}

\subsection{Trenched Grating}
